### 2019-07-17 response.tex

  {\it Changed as suggested.}
\item
  p.12 l.-10: Equation (2.4) is not only integrating both sides of (2.3), please explain more.

  {\it We added some explanations before (2.4).}
\item
  p.20 l.4: In the first equality in the denominator it has to be $y^{1+\gamma(\zeta_s)}$.

  {\it We think the referee means $y^{1+\gamma(\xi_s)}$.
    Changed as suggested. }
\item
  p.20 l.10 eq.(3.11): You don't need to add $x$ in the norm of $\|\kappa \gamma \phi^{\gamma - 1}\|$.

  {\it Done as suggested.}
\item
  p.20 eq.(3.13) and p.21 in 9 more times: You missed an $m$ in $\left\langle v, \phi^* \right\rangle_m$.

  {\it We added them as suggested.}
\item
  p.21 l.1: I will add: On the other hand, according to (3.2) and Proposition 3.2.

  {\it Added as suggested.}
\item
  p.23 l.-4: I will add then by Assumption 4, the spine representation, Campbell's formula...

  {\it Changed as suggested.}
\item
  p.25 eq.(3.27) and the next equation: I think that in your equations you missed a factorial, i.e.
  \begin{align}
    F_\alpha(\theta)
    \leq \frac{C^k}{k!} \left( \rho C+1 \right) \theta^k
  \end{align}
  and
  \begin{align}
    F_\alpha(\theta)
    \leq \frac{C^{k+1}}{(k+1)!} \left( \rho  C+1 \right) \theta^{k+1}
  \end{align}
  The reason is that in your next computation, Page 25 line -4 and -3. You missed an $\frac{1}{k+1}$ from the integration.
  In this case, you need to add a $\frac{1}{k}$ on the last equation of page 25.

@@

  {\it We give a new proof of this Lemma which is shorter and better.}
\item
  p.29 in step 3: I will add: Notice that, by (1.20) and since $\left\langle f, \phi^* \right\rangle_m = 1$.

  {\it Added as suggested.}
\end{enumerate}
\section*{Response to the comments of Referee 2}
\begin{enumerate}
\item
  {\bf (Important!)} General remark: There are a number of restrictive looking assumptions and thus it is crucial that the authors provide examples which are covered by the settings.
  It is true that before Assumption 4, there is a reference to [24] `for a list of examples,' but this is somewhat hidden.
  At least a brief summary of examples should be placed at a more visible spot that convinces the reader that the scope is not as restricted as it seems.

  In [24] there are indeed 12 examples given.
  I would at least vaguely describe (some of) these, possibly in an appendix and definitely without proofs, just mentioning that details and proofs (of these being examples) are in [24].
  If it is relegated to an appendix then somewhere at the beginning at a visible spot I'd refer the reader to the appendix.

  {\it We gave some examples in Appendix A.1 and we also referred the reader Appendix A.1 at the end of the paragraph  after Assumption 3.}
\item
  p.2 in the middle: define positively regular.

@@

  {\it We added a new sentence there which gives the function $\beta$.}
\item
  p.6 l.-15: Why isn't it $P_t^\beta \phi(x) = e^{\lambda t}\phi(x)$ and $P_t^{\beta*} \phi^*(x) = e^{\lambda t}\phi^*(x)$?

  {\it Should be $P_t^\beta \phi(x) = e^{\lambda t}\phi(x)$ and $P_t^{\beta*} \phi^*(x) = e^{\lambda t}\phi^*(x)$. Corrected as suggested.}
\item
  p.6 paragraph after Assumption 2: The notation is a bit confusing. So $\phi$ is the principal eigenfunction for the motion with the potential $\beta$ but $\varphi$ is the same without the potential.
  This should be made more clear.

  {\it We added a paragraph after Assumption 2 to make this more clear.
    Note that in the new version the notation $\varphi$ and $\varphi^*$ is changed into $\widetilde \phi$ and $\widetilde \phi^*$, respectively.}
\item
  Same place ({\bf Important!}): It is not clear why $\varphi$ is well defined.
  Let's say $\xi$ is a diffusion process.
  If $\mathcal L$ is the elliptic operator corresponding to it and $\lambda(\mathcal L)$ is its (generalized) principal eigenvalue then $\mathcal L - \lambda(\mathcal L)$ may or may not have a Green's function.
  In the second case everything is fine and $\varphi$ is uniquely determined up to constant multiples; it is the ground state.
  However, in the first case the cone of positive harmonic functions w.r.t. $\mathcal L - \lambda(\mathcal L)$ is not necessarily one dimensional.
  For example, if we know that $\xi$ is recurrent (and so $\lambda(\mathcal L) = 0$), then we are fine.
  But when it is transient, uniqueness does not follow.

  {\it

  Assumption 1 excludes the first case. We added a paragraph after Assumption 1
  which explains that the principal eigenfunction of the original semigroup $(P_t)_{t\ge0}$ is indeed well defined.
    Note that in the new version the notations $\varphi$ and $\varphi^*$ are changed into $\widetilde \phi$ and $\widetilde \phi^*$, respectively.}
\item
  p.8 l.6: I would rather say that the family of functions is just $(e^{\lambda t} \phi)_{t\geq 0}$, while $(e^{\lambda t} X_t(\phi))_{t\geq 0}$ is indeed the martingale.

### 2019-07-17 stableLimit.tex
change stableLimit.tex
See if I agree all the changes

	Urbana, IL 61801}

@@

%	School of Mathematical Sciences\\

@@

%	Peking University\\

@@

%	Beijing, P. R. China, 100871}
Wuhan, Hubei 430072, P. R. China}

@@

Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment
condition. Their main result can be stated as follows.
  Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a $d$-type, nonsingular Galton-Watson process with its mean matrix $M:= (E[Z_1^{(j)}| Z_0^{(i)} = 1, Z_0^{(k)} = 0, \forall k \neq i])_{1\leq i,j\leq d}$ being positive regular, that is, all entries of $M$ are finite and there exists a number $n \geq 1$ such that all entries of $M^n$ are positive.
Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
%Let the process be critical in the sense that the maximal eigenvalue of $M$ is $1$.
Assume that the process is critical in the sense that the maximal eigenvalue of $M$ is $1$.
Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to this maximal eigenvalue $1$, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, where $\mathbf 1$ is the vector $(1,\dots, 1)$.
Suppose that
\begin{align}
  \label{eq: regularly varying condition for multitype branching process}
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\end{align}
where $0 < \alpha \leq 1$;
$l$ is slowly varying at $0$;
and the matrix $G(\mathbf s)$ is defined by
\begin{align}
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\end{align}
Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\begin{align}
  \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
  n l(a_n)
	\operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{}
	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
\end{align}
and for each $\mathbf j \in \mathbb N_0^d$,
\begin{align}\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\end{align}
where $\mathbf z^{(\alpha)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev}.
For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
Vatutin \cite{Vatutin1977Limit} also considered analogous results for 
%the continuous time multitype critical Galton-Watson processes.
continuous time multitype critical Galton-Watson processes.

@@

In this paper, we are interested in a class of measure-valued branching Markov 
%process known as $(\xi, \psi)$-superprocesses:
processes known as $(\xi, \psi)$-superprocesses:
$\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact separable metric space $E$;
$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty)$ of the form
\begin{align} \label{eq: branching mechanism}
	\psi(x,z):=
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
	\quad x\in E, z\geq 0,
\end{align}
where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.

@@

It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
A simpler version of this question has already been answered in the context of continuous-state branching processes	(CSBPs) which can be viewed as superprocesses without spatial movements.
Kyprianou and Pardo \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
They showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\begin{align} \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\end{align}
where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and 
%is independent to the initial position $x$.
is independent of the initial position $x$.
Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
\begin{align}\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0,
\end{align}
where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\begin{align}\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
  \xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}
\end{align}
where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and 
%is independent to the initial position $x$.
is independent of the initial position $x$.

@@

In this paper, we will establish a result parallel to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocesses $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\begin{align}
	\psi(x,z)
  &= - \beta(x) z + \kappa(x) \int_0^\infty (e^{-z y} - 1+ z y) \frac{dy}{\Gamma(- \gamma(x)) y^{1+ \gamma(x)}}
  \\&=  -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\end{align}
where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
Let $\mu$ be an arbitrary finite initial measure on $E$.
We will show that $\mathbf P_{\mu}( \| X_t\| \neq 0)$ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we will show that
\begin{align}
	\lim_{t\to \infty}\eta^{-1}_t \mathbf P_{\mu}( \|X_t\| \neq0)
	= \mu(\phi),
\end{align}
and for a large class of non-negative testing functions $f$,
\begin{align}\label{eq: result2}
	\{ \eta_t X_t(f) ; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\end{align}
where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0-1$).
Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$
%does not depend the initial configuration $\mu$.
does not depend on the initial configuration $\mu$.
Precise statements of the assumptions and the results are presented in the next subsection.
It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $\{X; \mathbf P\}$ depends primarily on the lowest index $\gamma_0$.

@@

We first fix our notation.
%For any measurable space $(E,\mathscr E)$, we denote by $\mathscr E$ the collection of all real-valued measurable functions on $E$.
%Define $\mathscr E_b :=\{f \in \mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr E^+ :=\{f\in \mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $\mathscr E^{++} :=\{f\in \mathscr E: \forall x\in E,~f(x)> 0\}$.
%Define $\mathscr E^+_b := \mathscr E_b \cap \mathscr E^+$ and $\mathscr E^{++}_b:= \mathscr E_b \cap \mathscr E^{++}$.
%Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
%Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
%For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
%We also write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
%For any $f \in \mathscr E^+$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$.
%In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
%If $E$ is a topological space, we denote by $\mathscr B(E)$ the collection of all  Borel subsets of $E$.
Unless stated explicitly otherwise, $E$ is assumed to be a locally compact separable metric space. 
We use $\mathscr B(E)$ to denote the collection of all  Borel subsets of $E$ and also the collection of all  Borel functions on $E$. Define $\mathscr B_b(E) :=\{f \in \mathscr B(E): \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr B^+(E) :=\{f\in \mathscr B(E): \forall x\in E,~f(x)\geq 0\}$ and $\mathscr B^{++}(E) :=\{f\in \mathscr B(E): \forall x\in E,~f(x)> 0\}$.
Define $\mathscr B^+_b(E) := \mathscr B_b(E) \cap \mathscr B^+(E)$ and $\mathscr B^{++}_b(E):= \mathscr B_b(E) \cap \mathscr B^{++}(E)$.
Denote by $\mathcal M_E$ the collection of all Borel measures on $E$.
Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite Borel measures on $E$.
For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
For any $f \in \mathscr B^+(E)$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$. In particular, $\mathcal M^1_E$ is the collection of all  finite Borel measures on $E$.

We now give the definition of a $(\xi, \psi)$-superprocess:
%Let $E$ be a locally compact separable metric space, the spatial motion 
Let the spatial motion 
$\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by \eqref{eq: branching mechanism}.
We say an $\mathcal M^1_E$-valued Hunt process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
\begin{align}
	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
\end{align}
where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
\begin{align}\label{eq:FKPP_in_definition}
	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
	= \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
	\quad t \geq 0, x \in E.
\end{align}
(In this paper, for any real-valued function $F$ on $E\times [0,\infty)$ and real-valued function $f$ on $E$, we write $F(x,f):= F(x,f(x))$ for simplicity.)

@@

%moved from above
We will write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.
%end move

>>>>

	% Urbana, IL 61801}
	Urbana, IL, USA, 61801}

@@

@@

@@

% Wuhan, Hubei 430072, P. R. China}
Wuhan, Hubei, P. R. China, 430072}

@@

Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment
condition. Their main result can be stated as follows.
  Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a $d$-type, nonsingular Galton-Watson process with its mean matrix $M:= (E[Z_1^{(j)}| Z_0^{(i)} = 1, Z_0^{(k)} = 0, \forall k \neq i])_{1\leq i,j\leq d}$ being positive regular, that is, all entries of $M$ are finite and there exists a number $n \geq 1$ such that all entries of $M^n$ are positive.
Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
Assume that the process is critical in the sense that the maximal eigenvalue of $M$ is $1$.
Let $\mathbf v$ and $\mathbf u$ be the left and right  eigenvectors of $M$, respectively, corresponding to this maximal eigenvalue $1$, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, where $\mathbf 1$ is the vector $(1,\dots, 1)$.
Suppose that
\begin{align}
  \label{eq: regularly varying condition for multitype branching process}
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\end{align}
where $0 < \alpha \leq 1$;
$l$ is slowly varying at $0$;
and the matrix $G(\mathbf s)$ is defined by
\begin{align}
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\end{align}
Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\begin{align}
  \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
  n l(a_n)
	\operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{}
	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
\end{align}
and for each $\mathbf j \in \mathbb N_0^d$,
\begin{align}\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\end{align}
where $\mathbf z^{(\alpha)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev}.
For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
Vatutin \cite{Vatutin1977Limit} also considered analogous results for continuous time multitype critical Galton-Watson processes.

@@

In this paper, we are interested in a class of measure-valued branching Markov processes known as $(\xi, \psi)$-superprocesses:
$\xi$, the spatial motion of the superprocess, is a Hunt process on a locally compact separable metric space $E$;
$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty)$ of the form
\begin{align} \label{eq: branching mechanism}
	\psi(x,z):=
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
	\quad x\in E, z\geq 0,
\end{align}
where $\beta \in \mathscr B_b(E)$, $\alpha \in \mathscr B^+_b(E)$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ such that $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
For the precise definition and properties of superprocesses, see \cite{Li2011Measure-valued}.

@@

It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
A simpler version of this question has already been answered in the context of continuous-state branching processes	(CSBPs) which can be viewed as superprocesses without spatial movements.
Kyprianou and Pardo \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$, where $c > 0$ and $\gamma \in (1,2]$.
They showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\begin{align} \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\end{align}
where $\mathbf z^{(\gamma - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent of the initial position $x$.
Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
\begin{align}\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0,
\end{align}
where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\begin{align}\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
  \xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}
\end{align}
where the distribution of the random variable $\mathbf z^{(\gamma - 1)}$ is given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$) and is independent of the initial position $x$.

@@

In this paper, we will establish a result parallel to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocesses $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\begin{align}
	\psi(x,z)
  &= - \beta(x) z + \kappa(x) \int_0^\infty (e^{-z y} - 1+ z y) \frac{dy}{\Gamma(- \gamma(x)) y^{1+ \gamma(x)}}
  \\&=  -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\end{align}
where $\beta \in \mathscr B_b(E)$, $\gamma \in \mathscr B^+_b(E)$, $\kappa \in \mathscr B^+_b(E)$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
Let $\mu$ be an arbitrary finite initial measure on $E$.
We will show that $\mathbf P_{\mu}( \| X_t\| \neq 0)$ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $\frac{1}{\gamma_0 - 1}$.
Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we will show that
\begin{align}
	\lim_{t\to \infty}\eta^{-1}_t \mathbf P_{\mu}( \|X_t\| \neq0)
	= \mu(\phi),
\end{align}
and for a large class of non-negative testing functions $f$,
\begin{align}\label{eq: result2}
	\{ \eta_t X_t(f) ; \mathbf P_{\mu}(\cdot | \|X_t\|\neq 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\end{align}
where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa\cdot \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma_0-1$).
Notice that the distribution of the weak limit $\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)}$ does not depend on the initial configuration $\mu$.
Precise statements of the assumptions and the results are presented in the next subsection.
It is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $\{X; \mathbf P\}$ depends primarily on the lowest index $\gamma_0$.

@@

We first fix our notation.
Unless stated explicitly otherwise, $E$ is assumed to be a locally compact separable metric space. 
We use $\mathscr B(E)$ to denote the collection of all  Borel subsets of $E$ and also the collection of all  Borel functions on $E$. Define $\mathscr B_b(E) :=\{f \in \mathscr B(E): \sup_{x\in E}|f(x)|<\infty \}$, $\mathscr B^+(E) :=\{f\in \mathscr B(E): \forall x\in E,~f(x)\geq 0\}$ and $\mathscr B^{++}(E) :=\{f\in \mathscr B(E): \forall x\in E,~f(x)> 0\}$.
Define $\mathscr B^+_b(E) := \mathscr B_b(E) \cap \mathscr B^+(E)$ and $\mathscr B^{++}_b(E):= \mathscr B_b(E) \cap \mathscr B^{++}(E)$.
Denote by $\mathcal M_E$ the collection of all Borel measures on $E$.
Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite Borel measures on $E$.
For simplicity, we write $\mu(f)$ and sometimes $\langle \mu, f\rangle$ for the integration of a function $f$ with respect to a measure $\mu$.
For any $f \in \mathscr B^+(E)$, define $\mathcal M^f_E:= \{\mu \in \mathcal M_E: \mu(f) < \infty\}$. In particular, $\mathcal M^1_E$ is the collection of all  finite Borel measures on $E$.

We now give the definition of a $(\xi, \psi)$-superprocess:
Let the spatial motion 
$\xi=\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be an $E$-valued Hunt process with its lifetime denoted by $\zeta$, and the branching mechanism $\psi$ be a function on $E\times[0,\infty)$ given by \eqref{eq: branching mechanism}.
We say an $\mathcal M^1_E$-valued Hunt process $X=\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  $f\in \mathscr B^+_b(E)$, we have
\begin{align}
	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
\end{align}
where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is the unique locally bounded positive solution to the equation
\begin{align}\label{eq:FKPP_in_definition}
	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
	= \Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
	\quad t \geq 0, x \in E.
\end{align}
(In this paper, for any real-valued function $F$ on $E\times [0,\infty)$ and real-valued function $f$ on $E$, we write $F(x,f):= F(x,f(x))$ for simplicity.)

@@

We will write $\langle f, g\rangle_m$ for $\int_E fg dm$ to emphasize that it is the inner product in the Hilbert space $L^2(E, m)$.

Let $(P_t^*)_{t\geq 0}$ be the dual of the transition semigroup $(P_t)_{t\geq 0}$ in $L^2(E, m)$, i.e.,
\begin{align}
  P_0^* = I;
  \quad P_t^* f(x) := \int_E p_t(y,x) f(y) m(dy),
  \quad t > 0, x\in E, f\in \mathscr B_b(E).
\end{align}
Under Assumption \ref{asp: 1}, it is proved in \cite{RenSongZhang2015Limit} and \cite{RenSongZhang2017Central} that $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$ are both strongly continuous semigroups of compact operators in $L^2(E,m)$.
Let $\widetilde L$ and $\widetilde L^*$ be the generators of the semigroups $(P_t)_{t \geq 0}$ and $(P^*_t)_{t \geq 0}$, respectively.
Denote by $\sigma(\widetilde L)$ and $\sigma(\widetilde L^*)$ the spectra of $\widetilde L$ and $\widetilde L^*$, respectively.
According to \cite[Theorem V.6.6]{Schaefer1974Banach},
$\widetilde \lambda := \sup \text{Re}(\sigma(\widetilde L)) = \sup \text{Re}(\sigma(\widetilde L^*))$ is a common eigenvalue of multiplicity $1$ for both $\widetilde L$ and $\widetilde L^*$.
By the argument in \cite{RenSongZhang2015Limit},
the eigenfunctions $\widetilde \phi$ of $\widetilde L$ and $\widetilde \phi^*$ of $\widetilde L^*$ associated with the eigenvalue $\widetilde \lambda$ can be chosen to be strictly positive and continuous everywhere on $E$.
We further normalize $\widetilde \phi$ and $\widetilde \phi^*$ by $\big\langle \widetilde \phi, \widetilde \phi \big\rangle_m = \big\langle \widetilde \phi, \widetilde \phi^*\big\rangle_m = 1$ so that they are unique.
